A Capitalized Title: Something about a Package \pkg{cleanR}

### 2016-10-02 latex/article.tex
Rebirth
Small changes

<<>>=
library(cleanR)
data(testData)
testData
@

>>>>

\begin{Schunk}
\begin{Sinput}
> library(cleanR)
> data(testData)
> testData
\end{Sinput}
\begin{Soutput}
   charVar factorVar numVar intVar boolVar keyVar emptyVar _joeVar jack__var
1        a         a      1      1    TRUE      1        1       1         1
2        b         b      2      2   FALSE      2        1       2         2
3        c         c      3      3    TRUE      3        1       3         3
4        a         a      4      4    TRUE      4        1       4         4
5        b         b      5      5    TRUE      5        1       5         5
6        d         d      6      6   FALSE      6        1       6         6
7        a         a      7      7    TRUE      7        1       7         7
8        a         a      8      8   FALSE      8        1       8         8
9        b         b      9      9    TRUE      9        1       9         9
10       c         c     10     10    TRUE     10        1      10        10
11       a         a      1      1    TRUE     11        1      11        11
12       b         b      1      1   FALSE     12        1      12        12
13       d         d      1      1      NA     13        1      13        13
14       a         a      5      5      NA     14        1      14        14
15    <NA>       999      5      5      NA     15        1      15        15
   numOutlierVar smartNumVar      cprVar   cprKeyVar miscodedMissingVar
1              1           0 010101-1111 010101-1111                  .
2              2           0 020102-2929 020102-2929                   
3              3           0 121201-1902 121201-1902                nan
4              4           0 030729-2222 030729-2222                NaN
5              5           0 080909-1212 080909-1212                NAN
6              6           0 010101-1111 020202-0101                 na
7              7           0 020102-2929 030303-0101                 NA
8              8           1 121201-1902 040404-0101                 Na
9              9           1 030729-2222 050505-0101                Inf
10            10           1 080909-1212 060606-0101                inf
11            11           1 010101-1111 070707-0101               -Inf
12            12           1 020102-2929 080808-0101               -inf
13            13           1 121201-1902 090909-0101                  -
14            14           1 030729-2222 020202-0202                  9
15           100           1 080909-1212 030303-0202                  9
\end{Soutput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> clean(testData)
\end{Sinput}
\end{Schunk}

Arguments

\section{Extending the error checks}
